Group 9 Presentation

### 2021-12-07 presentation.Rmd
Presentation File/ Changes to LDA

library(ISLR)
library(leaps)
library(tidyr)
library(dplyr)
library(ggplot2)
library(glmnet)
library(caret)
library(pls) 
library(tree)
library(randomForest)
library(knitr)
library(class)
library(fastDummies)
library(reprtree)

@@

table("Preds"=preds$class, "True"=test$HeartDisease)
```

>>>>

library(ISLR)
library(leaps)
library(tidyr)
library(dplyr)
library(ggplot2)
library(glmnet)
library(caret)
library(pls) 
library(tree)
library(randomForest)
library(knitr)
library(class)
library(fastDummies)
library(reprtree)
library(MASS)
library(e1071)

@@

table("Preds"=preds$class, "True"=test$HeartDisease)

overall_LDA <- acc
overall_LDA

LDA_model
```
